AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-10-04 Paper/main.tex
10-4 fix paper

where $W$ denotes a non-negative weight vector acquired through a full connection layer, $W_i$ denotes the $i$-th dimension of the vector $W$. 

@@

Specifically, in our attention module they are calculated by the following equation

@@

The function $align()$ is as follows

@@

In our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in a biological sense. 
G is the damping matrix base on Gaussian function. 

>>>>

where $W\in\mathbb{R}^l$ denotes a non-negative weight vector acquired through a full connection layer, $W_i$ denotes the $i$-th dimension of the vector $W$. 

@@

As Figure~5\vphantom{\ref{fig:05}} show, in our attention module they are calculated by the following equation

@@

The function $align(\cdot)$ is as follows

@@

In our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense. 
$G\in\mathbb{R}^{l\times l}$ is the damping matrix base on Gaussian function. 
